---
title: "The Spark Foundation Task 1"
author: "RISHAB JAIN"
date: "06/01/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PROBLEM STATEMENT : 
## What will be the predicted score if studies for 9.25hr/day
Solution :
We will be using linear regression model for this prediction..
At first we will the load the library 
```{r}
library(tidyverse)
library(carat)
```
Now, we will load the dataset from the url given 
```{r}
library(readr)
scores <- read.csv("https://raw.githubusercontent.com/AdiPersonalWorks/Random/master/student_scores%20-%20student_scores.csv")
scores
```
#Now we will train the model
```{r}
hour <- scores$Hours
scr <- scores$Scores
model <- lm(scr~hour)
model
```
#Plotting the regression line
```{r}
attach(scores)
plot(Hours,Scores,type = "p",xlab = "Hours studied",ylab = "Percentage Scored",main = "Hours vs Percentage",col = "black")
abline(model,col = "green")
```
#Comparing the actual and predicted scores
```{r}
actual = scr
hour = data.frame(hour)
predicted <- predict(model,hour)
compare = data.frame(actual,predicted)
compare
```
## Now after training our model we can solve the question given in our task that what will be the score if it sudies for 9.25/days
```{r}
test = data.frame(hour = 9.25)
test2 = predict(model,test)
test2
```
# From this we come into conclusion that the prediction score for studying 9.25hrs/day is around 92.9 
